Synthesizing Quotient Lenses

### 2018-03-14 papers/QuotientLenses/main.tex
update cref options

% % Copyright information % Supplied to authors (based on authors' rights
% management selection; % see authors.acm.org) by publisher for camera-ready
% submission; % use 'none' for review submission.
\setcopyright{none}
\usepackage{algorithm, amsmath, amssymb, verbatim, enumerate, graphicx,
  centernot, tikz, array, mathtools, bussproofs, stmaryrd, enumitem,
  stackengine, subcaption, cleveref}
\captionsetup{compatibility=false}
\usepackage{relsize}
\usepackage{listings}
\usepackage{proof}
\usepackage{xspace}
\usepackage[noend]{algpseudocode}

>>>>

% % Copyright information % Supplied to authors (based on authors' rights
% management selection; % see authors.acm.org) by publisher for camera-ready
% submission; % use 'none' for review submission.
\setcopyright{none}
\usepackage{algorithm, amsmath, amssymb, verbatim, enumerate, graphicx,
  centernot, tikz, array, mathtools, bussproofs, stmaryrd, enumitem,
  stackengine, subcaption}
\captionsetup{compatibility=false}
\usepackage{relsize}
\usepackage{listings}
\usepackage{proof}
\usepackage{xspace}
\usepackage[noend]{algpseudocode}
\usepackage[capitalize]{cleveref}
